\section{Prestudy}
\subsection{Development methods}
\subsubsection{Scrum}
Scrum is an iterative and incremental development framework for development of complex information systems. The use of Scrum requires the team to be divided into specific roles, where each role has its own responsibility. The following is the core roles of the Scrum team:\\
\textbf{Product owner:} The product owner represents the stakeholders in the project, and is the voice of the customer. It is the product owner’s responsibility to ensure that the Scrum team at all times is working with the right things seen from a business perspective.\\
\textbf{Scrum master:} The scrum master should act as a buffer between the development team and distracting influences, so that the development team can deliver potentially shippable products at the end of each sprint. The scrum master should keep the development team focused at all times.\\
\textbf{Development team:} The development team is made up from three to nine persons with cross-functional skills. This team does the all the actual work, including development, testing, designing and so on.

\subsubsection{Spiral model}
The spiral model is software development model intended for large and complicated projects. It combines elements from the waterfall model and prototyping models, and uses an iterative approach. Based on this it allows for incremental releases of the product.

\subsubsection{Lean sofrware development}
Lean is an agile software development methodology that is defined by seven principles:\\
\textbf{Eliminate waste.} Everything that does not add any value to the customer is considered a waste.\\
\textbf{Amplify learning Defects} should be prevented by running early after the code is made.\\
\textbf{Decide as late as possible.} Better result should be achieved with an option-based approach. Delaying options as much as possible would give more flexibility later.\\
\textbf{Deliver as fast as possible-} The sooner the product is delivered, the sooner feedback can be received.\\
Empower the team The managers are taught how to listen to the developers, so they can explain better what action that might be taken, and give suggestion for improvement.\\
\textbf{Build integrity} in The customer needs to have more influence and inspection of the project.\\
\textbf{See the whole.} Decompose the system into smaller parts and find and eliminate defects.