\section{Testing}
	Testing is used to accomplish quality of the software and to avoid defects.
	
	\subsection{Testing strategy}

		\subsubsection{Unit testing}
			For the Android developing it was used Android testing API that is and extension of the JUnit API.
			This test aim at writing small portions of code, and check the results against expected results.

			In Android development, functions, contexts and Activities is a big portion of the coding.
			One small component is therefore one of these, and the unit testing is finish when these components are complete.

		\subsubsection{Integration testing}
			This test is based on combining different units and test the interface between them. It is a phase after the unit testing and before the validation testing. The units that can be used in these tests must therefore have passed the unit tests.

			Because our system is composed in more than one process (stk500 protocol and the market application), they 
			was tested in pair and not all at once.

			Integration testing identifies problems that occurs when we combine the units.

		\subsubsection{Validation testing}
			Validation testing is used for validating that the system have met the customers requirements.

		%This section might possible be removed
		\subsubsection{Functionality test}
			Functionality testing was used to test the specification of the software componenests.
			Functions are tested by give them inputs and examine the outputs, and it gives and indicator on what the system does.\\

			%Try to use functionality test when implementing stk500
			This was usfull when the STK500 was implemented.\\

			Functionality testing typically involves five steps:\\
			\begin{itemize}
			\item{The identification of functions that the software is expected to perform}
			\item{The creation of input data based on the function's specifications}
			\item{The determination of output based on the function's specifications}
			\item{The execution of the test case}
			\item{The comparison of actual and expected outputs}
			\end{itemize}

	\subsection{Usability and acceptance test}
		blablabla

	\subsection{System test}
		blablabla


\subsection{Bibliography}
	
	\subsubsection{Integration testing}
	\url{http://en.wikipedia.org/wiki/Integration_testing}
	\url{http://msdn.microsoft.com/en-us/library/aa292128(v=vs.71).aspx}

	\subsubsection{Functional testing}
	\url{http://en.wikipedia.org/wiki/Functional_testing}

	\subsubsection{Unit testing}
	\url{http://msdn.microsoft.com/en-us/library/aa292197(v=vs.71).aspx}
	\url{http://en.wikipedia.org/wiki/Unit_testing}
	\url{http://developer.android.com/tools/testing/testing_android.html}

	\subsubsection{Testing overview}
	\url{http://msdn.microsoft.com/en-us/library/aa292191(v=vs.71).aspx}

	\subsubsection{Validation testing}
	\url{http://en.wikipedia.org/wiki/Verification_and_validation}
	\url{http://www.buzzle.com/articles/validation-testing.html}