\section{Evalutation}
\subsection{Team roles}
The group was organized in different roles based on skill and experience. Each team member was given a responsibility for some code-packages. Further, the team was divided in six subgroups where each subgroup had one responsible leader. These were respectively group leader, documentation and substitute leader, arduino and PUI, Android and GUI, and test leader.

\subsubsection{Role evaluation}
The division of the group was an important feature. Every member knew who to contact about a specific problem, and who to contact regarding different tasks.
\begin{description}
	\item[Group leader]{was responsible the progress in the overall project. This person ensured progress and priorities for deadlines.}
	\item[Documentation and subsitute leader]{was responsible for management of documentation and reports. In absence of the group leader, this person took on the group leaders responsibilities. This person were also responsible for contact with the customer and supervisor. }
	\item[Android and GUI]{was responsible for the arduino part of the project. This implies contacting the arduino-lab, requirements of hardware and the coding part.This role were also responsible for development of the PUI examples.}
	\item[Arduino and PUI]{was responsible for the arduino part of the project. This implies contacting the arduino-lab, requirements of hardware, the coding part and over-the-air installation. This role were also responsible for development of the PUI examples.}
	\item[Over the air leader]{was responsible for programming the arduino over the air. This person was responsible for making the first prototype with a bluetooth connection.}
	\item[Test leader]{was responsible for developing and executing tests for the complete project.}
\end{description}
\begin{table}
\begin{tabular}{|l|l|}
\hline
	{\bf Name} & {\bf Role}\\
\hline
	Jeppe Benterud Eriksen & Group leader\\
\hline
	Nina Margrethe Smørsgård & Documantation and subsititue leader\\
\hline
	Robin Tordly & Android and GUI leader\\
\hline
	Bjørn Arve Fossum & Arduino and PUI leader\\
\hline
	Ståle Semb Hauknes & Over the air leader\\
\hline
	Wilhelm Walberg Schive & Test Leader\\
\hline
\end{tabular}
\caption{Roles}
\end{table}