

% We use MLA standard for citation. Create your citations at:
% http://citationmachine.net/index2.php?reqstyleid=0&stylebox=1

\begin{thebibliography}{9}

	\bibitem{scrum}{
		\emph{Scrum.org}.
		N.p.. Web. 13 Mar 2013
		<http://www.scrum.org/Resources/What-is-Scrum>.
		}

	%Citation for 'software engineering'
	\bibitem{sommerville}{
		Sommerville, Ian. \emph{Software Engineering}. 9th ed. Boston: Pearson Custom Publishing, 2011. Print.
	  	}

    \bibitem{poppendieck}{
        Poppendieck, M., and T. Poppendieck. \emph{Lean software development, an agile toolkit}. Addison-Wesley Professional, 2003. Print.
        }

    \bibitem{integration-testing1}{
    	\emph{Wikipedia.org}
    	<http://en.wikipedia.org/wiki/Integration\_testing>
    }

    \bibitem{integration-testing2}{
		\emph{Microsoft.com}
		<http://msdn.microsoft.com/en-us/library/aa292128(v=vs.71).aspx>
	}
	
	\bibitem{functional-testing}{
		\emph{Wikipedia.org}
		<http://en.wikipedia.org/wiki/Functional\_testing>
	}
	
	\bibitem{unit-testing1}{
		\emph{Microsoft.com}
		<http://msdn.microsoft.com/en-us/library/aa292197(v=vs.71).aspx>
	}
	
	\bibitem{unit-testing2}{
		\emph{Wikipedia.org}
		<http://en.wikipedia.org/wiki/Unit\_testing>
	}
	
	\bibitem{unit-testing3}{
		\emph{Android.com}
		<http://developer.android.com/tools/testing/testing\_android.html>
	}
	
	\bibitem{testing-overview}{
		\emph{Microsoft.com}
		<http://msdn.microsoft.com/en-us/library/aa292191(v=vs.71).aspx>
	}
	
	\bibitem{validation-testing1}{
		\emph{Wikipedia.org}
		<http://en.wikipedia.org/wiki/Verification\_and\_validation>
	}
	
	\bibitem{validation-testing2}{
		\emph{Buzzle.com}
		<http://www.buzzle.com/articles/validation-testing.html>
	}

    \bititem{kruchten}{
        Kroll, P., and P. Kruchten. \emph{The rational unified process made easy: A practitioner\'s guide to the rup}. Boston, MA: Addison-Wesley Professional, 2003. eBook.
        }

\end{thebibliography}
