% We use MLA standard for citation. Create your citations at:
% \url{http://citationmachine.net/index2.php?reqstyleid=0&stylebox=1

% Remember to update the bibliography number as you add or remove bibitems.
\thispagestyle{plain}

\begin{thebibliography}{21}

	\bibitem{baudrate}{
		\emph{electronicdesign.com}
		N.P.. Web. May 01 2013
		<\url{http://electronicdesign.com/communications/what-s-difference-between-bit-rate-and-baud-rate}>
	}

	\bibitem{kruchten}{
        Kroll, P., and P. Kruchten. \emph{The rational unified process made easy: A practitioner's guide to the rup}. Boston, MA: Addison-Wesley Professional, 2003. eBook.
    }

	\bibitem{scrum}{
		\emph{Scrum.org}.
		N.P.. Web. Mar 13 2013
		<\url{http://www.scrum.org/Resources/What-is-Scrum}>.
		}

	\bibitem{sommerville}{
		Sommerville, Ian. \emph{Software Engineering}. 9th ed. Boston: Pearson Custom Publishing, 2011. Print.
	  	}

    \bibitem{poppendieck}{
        Poppendieck, M., and T. Poppendieck. \emph{Lean software development, an agile toolkit}. Addison-Wesley Professional, 2003. Print.
        }

    \bibitem{rn-42}{
	\emph{Sparkfun.com}
	N.P.. Web. 
    <\url{https://www.sparkfun.com/products/10393}>.
    }

	\bibitem{hc-05}{
	\emph{Iteadstudio.com}
	N.P.. Web. 
	<\url{ftp://imall.iteadstudio.com/Modules/IM120723009/DS\_IM120723009.pdf}>.
    }

	\bibitem{testing-overview}{
		\emph{Microsoft.com}.
		N.P.. Web. Mar 13 2013
		<\url{http://msdn.microsoft.com/en-us/library/aa292191(v=vs.71).aspx}>
	}

		\bibitem{unit-testing1}{
		\emph{Microsoft.com}.
		N.P.. Web. Mar 13 2013
		<\url{http://msdn.microsoft.com/en-us/library/aa292197(v=vs.71).aspx}>
	}
	
	\bibitem{unit-testing2}{
		\emph{GeoSoft.no}.
		N.P.. Web. Mar 13 2013
		<\url{http://geosoft.no/development/unittesting.html}>
	}

	\bibitem{unit-testing3}{
		\emph{Android.com}.
		N.P.. Web. Mar 13 2013
		<\url{http://developer.android.com/tools/testing/testing\_android.html}>
	}

	\bibitem{Nielsen}{
		Nielsen, Jakob. ``Why you only need to test with 5 users.'' \emph{NNgroup.com}. N.P., Mar 19 2000. Web. 16 Apr 2013. <\url{http://www.nngroup.com/articles/why-you-only-need-to-test-with-5-users/}>.
	}


    \bibitem{AVR068}{
        \emph{Atmel.com}.
        N.P.. Web. Feb 8 2013
        <\url{http://www.atmel.com/Images/doc2591.pdf}>
    }
    
    \bibitem{StkBoot}{
		\emph{Google.com}
		N.P.. Web. Mar 25 2013
		<\url{https://code.google.com/p/stkboot/}>
	}
	
	\bibitem{uOS-Embedded}{
		\emph{Google.com}
		N.P.. Web. Mar 25 2013
		<\url{https://code.google.com/p/uos-embedded/}>
	}

    \bibitem{AVR061}{
        \emph{Atmel.com}.
        N.P.. Web. Mar 26 2013
        <\url{http://www.atmel.com/Images/doc2525.pdf}>
    }
    	
	\bibitem{validation-testing}{
		\emph{Buzzle.com}.
		N.P.. Web. Mar13 2013
		<\url{http://www.buzzle.com/articles/validation-testing.html}>
	}
    	
    \bibitem{integration-testing2}{
		\emph{Microsoft.com}.
		N.P.. Web. Mar 13 2013
		<\url{http://msdn.microsoft.com/en-us/library/aa292128(v=vs.71).aspx}>
	}
	
	%todo: remove?
	\bibitem{functional-testing}{
		\emph{Wikipedia.org}.
		N.P.. Web. Mar 13 2013
		<\url{http://en.wikipedia.org/wiki/Functional\_testing}>
	}

    \bibitem{android-dev-guide}{
    	\emph{Android.com}
    	N.P.. Web. May 5 2013
    	<\url{http://developer.android.com/design}>
    }

    \bibitem{git-branch}{
    	\emph{http://git-scm.com/}
    	N.P.. Web. May 12 2013
    	<\url{http://git-scm.com/book/en/Git-Branching-What-a-Branch-Is}>
    }

    \bibitem{websequencediagrams}{
    	\emph{http://www.websequencediagrams.com/}
    	N.P.. Web. May 12 2013
    	<\url{http://www.websequencediagrams.com/}>
    }



	\bibitem{download-arduino}
		\emph{Arduino.cc}
		N.P.. Web. 
		<\url{http://arduino.cc/en/Main/Software}>

	\bibitem{download-computerserial}{
		\emph{Github.com}
		N.P.. Web. May 9 2013
		<\url{https://github.com/Prosjekt2-09arduino/ArduinoStore/tree/master/Arduino/ComputerSerial/}>
	}
	
	\bibitem{import-libraries}{
		\emph{Arduino.cc}
		N.P.. Web. Mar 24 2013
		<\url{http://arduino.cc/en/Guide/Libraries/}>
	}
	
	\bibitem{rn-42-at-commands}{
		\emph{Sparkfun.com}
		N.P.. Web. Feb 21 2013
		<\url{https://www.sparkfun.com/datasheets/Wireless/Bluetooth/rn-bluetooth-um.pdf}>
	}
	
	\bibitem{hc-05-at-commands}{
		\emph{Elecfreaks.com}
		N.P.. Web. Feb 21 2013
		<\url{http://elecfreaks.com/store/download/datasheet/Bluetooth/HC-0305%20serail%20module%20AT%20commamd%20set%20201104%20revised.pdf}>
	}
	
	\bibitem{arduino-tutorials}{
		\emph{Arduino.cc}
		N.P.. Web. Mar 24 2013
		<\url{http://arduino.cc/en/Tutorial/HomePage}>
	}

    
    \section*{Source of images}
    This section containts the all the sources for all the images used in the report. The images and sources that are not listed here is made by the project team. \\

    Figure~\ref{fig:sintef} in section~\ref{sec:sintef} : \\
    N.P.. Web. Apr 19 2013\\
	<\url{http://www.sintef.no}> \\

	Figure~\ref{fig:ntnu} in section~\ref{sec:ntnu} : \\
	N.P.. Web. Apr 19 2013\\
	<\url{http://www.ntnu.no}> \\

	Figure~\ref{fig:googleplay} in section~\ref{sec:googleplay} \\
	N.P.. Web. Mar 13 2013\\
	<\url{http://droidtrends.com/wp-content/uploads/2012/07/Google-Play-Store-APK-3.7.15.jpg}> \\

	Figure~\ref{fig:pebblewatch} in section~\ref{sec:pebblewatch} : \\
	N.P.. Web. Apr 19 2013\\
	<\url{http://getpebble.com/}> \\

	Figure~\ref{fig:SimpleArduinoWiring} in section~\ref{sec:SimpleArduinoWiring} : \\
	N.P.. Web. Apr 19 2013\\
	<\url{http://fritzing.org/}> \\

	Figure~\ref{fig:rup} in section~\ref{sec:rup} \\
	N.P.. Web. Apr 19 2013\\
	<\url{http://www.c3ns.com/c3nsservices_3.html}> \\
	
\end{thebibliography}
