\subsection{Registered trademarks}

\begin{description}
	\item[Android$\texttrademark$]\hfill \\
		Android is a trademark of Google Inc. \newline
		The Android robot is reproduced or modified from work created and shared by Google and used according to terms described in the Creative Commons 3.0 Attribution License.
	\item[Apache$\texttrademark$]\hfill \\
		Apache is a trademark and service mark by ASF Projects for community developed open source software products.
	\item[Arduino$\texttrademark$]\hfill \\
		Arduino is a trademark of Arduino team.
	\item[Atmel$\textsuperscript{\textregistered}$]\hfill \\
		Atmel, AVR$\textsuperscript{\textregistered}$061 and AVR$\textsuperscript{\textregistered}$062 are registered trademarks or trademarks of Atmel Corporation or its subsidiaries, in the US and/or other countries.
	\item[Bluetooth$\textsuperscript{\textregistered}$]\hfill \\
		The Bluetooth word mark, figure mark, combination mark, and Bluetooth Smart and Bluetooth Smart Ready marks are all trademarks that are owned by the Bluetooth SIG and licensed out for use to companies that are incorporating Bluetooth wireless technology into their products. 
	\item[Doodle$\texttrademark$]\hfill \\
		Doodle is a trademark of  Doodle AG.
	\item[Dropbox$\texttrademark$]\hfill \\
		Dropbox is a trademark of Dropbox.
	\item[Eclipse$\texttrademark$]\hfill \\
		 Eclipse is a trademark of the Eclipse Foundation.
	\item[Fritzing$\texttrademark$]\hfill \\
		Fritzing is a trademark of the Friends-of-Fritzing e.V.
	\item[Google$\texttrademark$]\hfill \\
		Google, Google Calendar$\texttrademark$, Google Docs$\texttrademark$ and Google Play$\texttrademark$ are trademarks of Google Inc.
	\item[Microsoft$\textsuperscript{\textregistered}$]\hfill \\
		 Microsoft and Microsoft Word$\textsuperscript{\textregistered}$ are trademarks of Microsoft Corp.
	\item[OmniGraffle$\texttrademark$]\hfill \\
		OmniGraffle is a trademark of Apple Inc.
	\item[Raspberry Pi$\textsuperscript{\textregistered}$]\hfill \\
		Raspberry Pi is a trademark of the Raspberry Pi Foundation.
	\item[TexMate$\texttrademark$]\hfill \\
		TextMate is a trademark of Allan Odgaard.
	\item[SQLite$\texttrademark$]\hfill \\
		SQLite is a trademark of Hwaci.
	\item[QR Code$\textsuperscript{\textregistered}$]\hfill \\
		QR Code is a registered trademark of Denso Wave.
\end{description}